---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sspower

<!-- badges: start -->
<!-- badges: end -->

The goal of sspower is to provide functions to compute sample size and power for studies that will be analyzed using generalized linear models and from time-to-event regression models, including the Cox proportional hazards and Fine-Gray models. 

## Installation

The current version of sspower is available in this repository. If you have the R package “devtools” installed, sspower can be installed directly from GitHub with:

``` r
require(devtools)
install_github("mjmartens/sspower")
```

## Example

Suppose we want to estimate the sample size needed for a joint test of the effects of two main variable in a logistic regression model while adjusting for other covariates. The test will have a 5% significance level and 80% power. Log odds ratios targeted for the variables are 0.5 and 0.3. The main variables are assumed to be independent with variances 0.5 and 0.25. The coefficient of determination matrix (R2) is assumed to be diag(c(0.,0.5)). The expected residual variance E[Var(Y|X)] is specified as 0.2. 

Sample size calculation proceeds as follows from the ssGLM function:

```{r example}
library(sspower)
level = 0.05
pow = 0.80
del = c(0.5,0.3)
vz = diag(c(0.5,0.25))
rsq = diag(c(0,0.5))
f0 = 0.20

ssGLM(level,pow,del,vz,rsq,f0)

```

Approximately 354 patients in total are required for this study.
